descriptive anaysis

### 2020-06-10 src/bbData2020.Rmd

```{r echo=FALSE, results= 'asis', message=FALSE, warning=TRUE}
#create 2 dataframes for 2 matching periods
Wks2019 <- selectByDate(bb2020, start = "2019-01-21", end = "2019-06-02")
names(Wks2019)[1:2] <- c("dateOnly", "date") #413788 obs
Wks2020 <- selectByDate(bb2020, start = "2020-01-20", end = "2020-05-31")
names(Wks2020)[1:2] <- c("dateOnly", "date") #521773 obs
#timeplots
TimeVar2019 <- timeVariation(Wks2019, pollutant = "speeddown", statistic = "mean", name.pol = "speedown 2019")
TimeVar2019up <- timeVariation(Wks2019, pollutant = "speedup", statistic = "mean", name.pol = "speedup 2019")
TimeVar2020 <- timeVariation(Wks2020, pollutant = "speeddown", statistic = "mean", name.pol = "speeddown 2020")
TimeVar2020up <- timeVariation(Wks2020, pollutant = "speedup", statistic = "mean", name.pol = "speedup 2020")
timePlot(Wks2019, pollutant = "speeddown", avg.time = "day", smooth = TRUE, name.pol = "speeddown 2019")
timePlot(Wks2020, pollutant = "speeddown", avg.time = "day", smooth = TRUE, name.pol = "speeddown 2020")
timePlot(Wks2019, pollutant = "speedup", avg.time = "day", smooth = TRUE, name.pol = "speedup 2019")
timePlot(Wks2020, pollutant = "speedup", avg.time = "day", smooth = TRUE, name.pol = "speedup 2020")
```

@@

```{r echo=FALSE, results= 'asis', message=FALSE, warning=TRUE}

@@

Plot2019 + geom_line()
Plot2020 <- ggplot(Wks2020, aes(dateOnly, tests20))
Plot2020 + geom_line()
HrDateCount19 <- count(Wks2019, dateOnly, hour)
HrDateCount20 <- count(Wks2020, dateOnly, hour)
names(HrDateCount19)[3] <- "testFreq19"
names(HrDateCount20)[3] <- "testFreq20"
Wks2019 <- left_join(Wks2019, HrDateCount19)
Wks2020 <- left_join(Wks2020, HrDateCount20)
TimeVar2019n <- timeVariation(Wks2019, pollutant = "testFreq19", 
                    statistic = "mean")
TimeVar2020n <- timeVariation(Wks2020, pollutant = "testFreq20", 
                              statistic = "mean")
#save files
write.csv(Wks2019, "Wks2019.csv")
write.csv(Wks2020, "Wks2020.csv")

@@

# Spatial analysis

```{r echo=FALSE, results= 'asis', message=FALSE, warning=TRUE}

>>>>

```{r echo=FALSE, results= 'asis', message=FALSE, warning=TRUE, fig.height=15, fig.width=15}
#OLD# #add column for day of the week
#OLD# bb2020$weekday <- wday(bb2020$date, label = TRUE)

#create 2 dataframes for 2 matching periods
Wks2019 <- selectByDate(bb2020, start = "2019-01-21", end = "2019-06-02")
names(Wks2019)[1:2] <- c("dateOnly", "date") #413788 obs
Wks2020 <- selectByDate(bb2020, start = "2020-01-20", end = "2020-05-31")
names(Wks2020)[1:2] <- c("dateOnly", "date") #521773 obs
#timeplots
TimeVar2019 <- timeVariation(Wks2019, pollutant = "speeddown", statistic = "mean", name.pol = "speedown 2019")
TimeVar2019up <- timeVariation(Wks2019, pollutant = "speedup", statistic = "mean", name.pol = "speedup 2019")
TimeVar2020 <- timeVariation(Wks2020, pollutant = "speeddown", statistic = "mean", name.pol = "speeddown 2020")
TimeVar2020up <- timeVariation(Wks2020, pollutant = "speedup", statistic = "mean", name.pol = "speedup 2020")
timePlot(Wks2019, pollutant = "speeddown", avg.time = "day", smooth = TRUE, name.pol = "speeddown 2019")
timePlot(Wks2020, pollutant = "speeddown", avg.time = "day", smooth = TRUE, name.pol = "speeddown 2020")
timePlot(Wks2019, pollutant = "speedup", avg.time = "day", smooth = TRUE, name.pol = "speedup 2019")
timePlot(Wks2020, pollutant = "speedup", avg.time = "day", smooth = TRUE, name.pol = "speedup 2020")
```

@@

```{r echo=FALSE, results= 'asis', message=FALSE, warning=TRUE, fig.height=15, fig.width=15}

@@

#OLD# timePlot(Wks2019, pollutant = "test19", avg.time = "hour", smooth = TRUE, name.pol = "hourlyTests 2019")
#OLD# timePlot(Wks2020, pollutant = "test20", avg.time = "hour", smooth = TRUE, name.pol = "hourlyTests 2020")
#OLD# TimeVar2019n <- timeVariation(Wks2019, pollutant = "test19", statistic = "mean", name.pol = "hourlytests 2019")
#OLD# TimeVar2020n <- timeVariation(Wks2020, pollutant = "test20", statistic = "mean", name.pol = "hourlytests 2020")
#OLD# Plot2019 <- ggplot(DateCount19, aes(Date19, tests19))

Plot2019 + geom_line()
Plot2020 <- ggplot(Wks2020, aes(dateOnly, tests20))
Plot2020 + geom_line()
HrDateCount19 <- count(Wks2019, dateOnly, hour)
HrDateCount20 <- count(Wks2020, dateOnly, hour)
names(HrDateCount19)[3] <- "testFreq19"
names(HrDateCount20)[3] <- "testFreq20"
Wks2019 <- left_join(Wks2019, HrDateCount19)
Wks2020 <- left_join(Wks2020, HrDateCount20)
TimeVar2019n <- timeVariation(Wks2019, pollutant = "testFreq19", 
                    statistic = "mean")
TimeVar2020n <- timeVariation(Wks2020, pollutant = "testFreq20", 
                              statistic = "mean")
#save files
write.csv(Wks2019, "Wks2019.csv")
write.csv(Wks2020, "Wks2020.csv")

@@

## Spatial analysis

<!-- # Ctrl + Shift + c to remove all the below comments -->
<!-- ```{r echo=FALSE, results= 'asis', message=FALSE, warning=TRUE, fig.height=15, fig.width=10} -->
<!-- #convert to spatial object -->
<!-- coords_bb <- cbind(bb2020$lon, bb2020$lat) -->
<!-- bbNUTS3 <- SpatialPointsDataFrame(coords_bb, data = data.frame(bb2020)) -->
<!-- proj4string(bbNUTS3) <- CRS("+init=epsg:4326") #define projection -->

<!-- #get NUTS3 from up a level and read in (145 NUTS3) -->
<!-- NUTS3 <- readOGR("../NUTS_Level_3_January_2015_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp") -->
<!-- NUTS3 <- spTransform(NUTS3, CRS("+init=epsg:4326")) -->
<!-- NUTS3@data$nuts315nm <- as.character(NUTS3@data$nuts315nm) -->

<!-- #spatial join to NUTS3 -->
<!-- bbNUTS3sp <- over(bbNUTS3, NUTS3[, "nuts315nm"]) #not a spatial object -->
<!-- bbNUTS3$nuts315nm <- bbNUTS3sp$nuts315nm -->

<!-- #create dataframe object to analyse (remove lat and lon?) -->
<!-- bb2020sp <- bbNUTS3@data -->
<!-- #% obs NA for NUTS3? -->

<!-- #summarise by date and geography -->
<!-- NUTS3datecount <- count(bb2020sp, nuts315nm, date) -->
<!-- NUTS3dateAvg <- summarise(group_by(NUTS3datecount, nuts315nm), mean(n)) -->

<!-- #map NUTS3 mean test frequency per date -->
<!-- NUTS3@data <- left_join(NUTS3@data, NUTS3dateAvg, by = "nuts315nm") -->
<!-- var <- NUTS3@data[ ,'mean(n)'] -->
<!-- breaks <- classIntervals(var, n = 5, style = "quantile") -->
<!-- my_colours <- brewer.pal(5, "Blues") -->
<!-- plot(NUTS3, col = my_colours[findInterval(var, breaks$brks, all.inside = TRUE)], axes = FALSE, -->
<!--      border = rgb(0.8, 0.8, 0.8, 0)) -->
<!-- legend(x = "top", legend = leglabs(breaks$brks), fill = my_colours, bty = "n", cex = 0.5) -->
<!-- ``` -->
